Research related to this paper can be divided into two groups. The first group is related to research on opinion or sentiment analysis of user reviews on mobile applications. The second group is related to analysis of texts written in Thai language.

\subsubsection{Research on opinion mining and sentiment analysis of user reviews of mobile applications} There are various researches in this group. Most of them analyzed user reviews written in English on mobile applications. We will discuss three of these works \cite{ar-miner,userslikefeature,keywordmining}. 

Chen et al.\cite{ar-miner} presented an AR-Miner framework which filtered reviews and extracted only informative reviews using a classification technique called Expectation Maximization for Naive Bays (EMNB) \cite{EMNB}, which is a semi-supervised machine learning algorithm. The remaining informative reviews were then grouped into topics. The work applied two topic modeling techniques, Latent Dirichlet Allocation (LDA) \cite{LDA} and Aspect and Sentiment Unification Model (ASUM) ~\cite{asum}, and compared results of these techniques.

Gunzmam and Laalej \cite{userslikefeature} analyzed user reviews to identify features and extract user sentiments associated with the features. Identifying features were done by finding expressions of two or more words that commonly occur together such as <\textit{view picture}>, or <\textit{user interface}>. User sentiments were analyzed using SentiStrength \cite{SentiStrength} for lexical sentiment extraction. Finally, LDA was used to group various features into coherent topics. The approach was evaluated with precision and recall values where the truth set was created by the two authors and other seven trained coders who manually analyzed user reviews. 

Minh et al. \cite{keywordmining} presented a semi-automated framework for mining user reviews given keywords specified by an analyst. The approach can also automatically extract keywords from user reviews by looking nouns and verbs. The keywords were clustered and expanded, and then used to search for relevant reviews hopefully containing useful opinions. The evaluation was done by comparing analysis results with eight computer science researchers.

This paper is similar to these researches, especially Gunzmam and Laalej's work, since we aim to analyze user reviews of mobile applications to extract features and user sentiments about them. These researches however analyzed user reviews written in English whereas our work focuses on user reviews written in Thai. Processing Thai texts is more difficult since Thai texts need to be segmented into sentences and words. In addition, there is no exical sentiment extraction tool like SentiStrength for Thai language. 

\subsubsection{Research on text mining of Thai texts} Several works have done researches on processing Thai texts for various purposes. Four works are discussed here.

Inrak and Sinthupinyo \cite{emotioninthai} applied latent semantic analysis (LSA) \cite{LSA} to classify Thai texts into six emotions: anger, disgust, fear, happiness, sadness, and surprise. They used the SWATH \cite{SWATH} tool for word segmentation and used the ORCHID \cite{ORCHID} corpus to help tag part of speech (POS).

In 2010, Haruechaiyasak et al. \cite{thaiopinionmininghotel} did opinion mining and sentiment analysis of hotel reviews written in Thai based on pre-determined features such as breakfast or service. From these features, related lexicons and a set of syntactic rules based on frequently occurred patterns were created to mine opinions and sentiments about these features.

In 2013, Haruechaiyasak et al. \cite{ssense,ssense2} presented S-Sense, a framework for analyzing sentiment on Thai social media contents. The framework crawled and collected texts from social media such as twitter and pantip, a popular Thai webboard, and did basic text processing such as sentence segmentation and tokenization. It then classified texts into a predefined set of topics, and provided intention analysis to classify each text into four classes: announcement, request, question and sentiment. The sentiments were further classified into positive and negative. Their subsequent work \cite{ssense2} generalizes by extracting and analyzing keywords with statistical sigificance from social media contents.

Leopairote et al. \cite{Leopairote1,Leopairote2} evaluated software quality in use by performing opinion mining of user reviews. Their approach constructed an ontology from the quality in use model, which is one of software quality models in ISO 9126, consisting of 4 characteristics: effectiveness, productivity, safety, satisfaction. Sentences in user reviews were then manually matched with terminologies defined in the ontology. To classify polarity of sentences into positive, negative, or neutral, the approach used sentences labeled to be pros and cons reviews and also used two lists of sentiment words to construct rule-based classifiers.

All works that process Thai texts have similar text processing steps such as word segmentation and part of speech tagging. Inrak and Sinthupinyo's work \cite{emotioninthai} has a quite different purpose since it focuses on emotions while the other works \cite{thaiopinionmininghotel,ssense,ssense2,Leopairote1,Leopairote2} extract various forms of information such as opinions and quality in use as well as sentiments. Our work is more simlar to the latter. There are some differences however. Haruechaiyasak et al. \cite{thaiopinionmininghotel} on hotel reviews has pre-determined features where ours dynamically extracts features from comments. The S-Sense framework \cite{ssense} analyzes keywords and sentiments from social media. Ours is similar but we group keywords using LDA since some keywords can be grouped into similar features. Lastly, Leopairote et al.'s work \cite{Leopairote1, Leopairote2} aims similarly to analyze user reviews of software products. Their work however focuses on overall quality in use of the software products whereas ours wants to drill down to opinions and sentiments on features of software products.



