
Electronic devices especially smart phones and tablets are used so commonly nowadays that they could have been parts of our bodies. Mobile applications are therefore in demand and have been developed increasingly. To make mobile applications desirable, not only must developers follow their own visions, but they should also listen to user feedbacks to understand what users want in mobile applications.

By listening to user feedbacks and improve mobile applications accordingly, resulting applications would suit users better and even attract more users, otherwise users might stop using applications and in the end there might be no one using the applications at all. According to the survey \cite{145Q} that asked software engineers to rate and identify important questions about software engineering practices, the second most "essential" question software engineers wanted to know was "What parts of a software product are most used and/or loved by customer?" The answer to this question is very useful for developers in order to add, remove, or improve their application features and ultimately satisfy user needs.

One way to answer this question is to analyze user comments or reviews in application stores such as Apple App Store or Google Play Store. Users usually write reviews to praise or complain about mobile applications allowing other users to assess quality of the applications and enabling developers to get user feedbacks and improve application features. 

However, with so many user reviews, it is difficult or takes too much time to comprehend what users feel about mobile applications. Some comments might not be informative. For example, comments such as "ดี" (meaning "good") cannot tell specifically which part of the application is good. In addition, product rating cannot tell all the stories; it can only provide overall application quality but cannot give details which features users like or do not like.

Consequently, there are a number of researches on automatic analysis of user comments on mobile applications \cite{ar-miner,userslikefeature,keywordmining}. Chen et al.\cite{ar-miner} extracted informative reviews and grouped them into topics using Latent Dirichlet Allocation (LDA) \cite{LDA}, a topic modeling technique. Gunzmam and Laalej \cite{userslikefeature} did research on sentiment analysis of application reviews using LDA \cite{LDA} for topic modeling and SentiStrength \cite{SentiStrength} for lexical sentiment extraction. Minh et al. \cite{keywordmining} used a keyword-based approach for semi-automated review analysis.

These researches analyzed user reviews written in English. This paper however aims to analyze user reviews written in Thai using LDA to group reviews into topics or features and analyzing sentiments to reveal which features users like or do not like. Although the approach is similar to Gunzmam and Laalej's work \cite{userslikefeature}, processing reviews written in Thai are more difficult since Thai texts need to be segmented into sentences and words. In addition, there is no  lexical sentiment extraction tool like SentiStrength for Thai language. 

There are also researches on analyzing user reviews in Thai. Haruechaiyasak et al. \cite{thaiopinionmininghotel} did sentiment analysis of hotel reviews written in Thai based on pre-determined topics such as breakfast or services whereas features in our work, by contrast, are grouped dynamically with LDA. More discussion on related work is presented in Section \ref{Related Work}.

The remaining of this paper is organized as follows. Section \ref{Background} lays out theories needed for review analysis. Section \ref{Related Work} describes related work in more details. Section \ref{Approach} presents our approach. Secton \ref{Result} discusses our results. Section \ref{Conclusion} provides conclusion and future works. 
%Please also note that this paper uses the word comments and reviews interchangeably.